\normallinespacing
\chapter{Introduction}

As technology continues to advance, there has been a dramatic explosion of digital content that is accessible online. Due to the sheer volume of accessible information, it is often overwhelming for users to find the right information. To alleviate the tedious act of filtering through online digital multimedia content, mathematical algorithms have been created to match relevant content, then score and rank the relevancy of the content with respect to the searching entity, creating recommendation systems. 

Recommendation systems filter through the most relevant pieces of content which provide structured recommendations which are relevant to the information it observes. \cite{Jannach2022} Though they are task specific and vary based off the setting they are used in, the specialized algorithms, in personalizing content for every user. Recommendation systems are such a powerful algorithm, that they must be monitored and structured properly. That's why for cases like the YouTube\cite{Davidson2010TheYV}, Netflix\cite{gomez2015netflix}, Pinterest \cite{ying2018graph} algorithms, where the recommendation is directly related to the service of the company, are used like products for the users to discover personalized content with.

These companies use this business model to advertise and tailor suggestions for their products to increase user retention and engagement, hence increasing revenue. \cite{lu2012recommender} As a result of this model, recommendation systems have been seen as potentially dangerous as they have the ability to influence users poorly. This ideology that recommendation systems have the capability to mislead users has led the academic community to research different ways for measuring bias, fairness, and privacy in recommendation systems. \cite{milano2020recommender}

Streaming platforms such as Spotify, Apple Music, or Amazon Music, are huge proponents of using recommendation systems. Music recommendation research is a competitive research field whose goal is to produce not only fair and unbiased music recommendations, but to provide users with relevant and interesting content. The main objective for these services is to retain loyalty of their users. \cite{jacobson2016music} The strategic mindset of competing companies like these, is to offer users a music recommendation service that is more engaging than the recommendation services provided by the other companies. 

The research field of music recommendation systems is largely supported by the academic community of music information retrieval (MIR), as well as the larger recommendation systems community. These communities have similar interests, which have often produced useful insights that modern day music streaming services utilize to form better music recommendation.

To provide examples of recent MIR research, newer discovering been able identified 3 styles of listening behaviors that consumers utilize MRS for; Basic Music Recommendation, Lean-in experiences, and Lean-back experiences. Where basic recommendation helps users find the content they may be searching for, Lean-in recommendation assists the engaged user typically associated with exploratory listening habits, and Lean-back recommendation helps users who wish to listen to music all day \cite{schedl2022music}. 

Music streaming services utilize a barrage of different methods to collect explicit and implicit data from user interactions. Explicit feedback includes information on when users like, rate, or save a piece of content, its very difficult to obtain a large summation of explicitly labeled content due to data sparsity issues. Since explicit feedback often is tedious to collect, implicit user feedback, or data collected on user listening events, clicks, skips are collected. As the user interacts with the platform more frequently, the preferences elicited from the listening behaviors of the user can be predicted. 

Often times this information is stored in an interaction database where a user will be labelled has having a connection to this piece of connect. This information does not indicate an explicit opinion from the user, rather as the user interacts with the platform more frequently, the preferences elicited from the listening behaviors of the user can be inferred. 

\input{intro/motivation}
\input{intro/structure}