\section{Motivation}
The way music streaming services utilize explicit and implicit information also comes in a variety of forms. The most common approaches for music-based recommendations would be content and collaborative filtering methods. These have been utilized for decades and proven to be effective for finding content that is relevant for a given task. Specifically, to highlight collaborative filtering, it is a recommendation system approach which leverages the explicit information to predict interactions that users have not yet experienced but are calculated as likely to occur.

As recommendation systems have improved significantly in the last decade, users are often given personalized recommendations based on much more than just their explicit feedback with content. Modern day recommendation systems often use newer methodologies, complex mathematics, machine learning and/or artificial intelligence to alleviate the pitfalls of traditional content and collaborative filtering methods such as interaction user modeling, the cold-start problem, robustness, and the ability to explain why recommendations are made. \cite{Zhang2022}

The most notably for this thesis, modern recommendation system approach involves using graph-based deep learning. This unique direction includes methods such as nonlinear transformation, representation learning, and sequence modeling which have become widely successful as well as accepted by the academic community. \cite{Zhang2022} Though the method is quite resourceful, there are some apart deterrents of industrial level implementation due to the “black-box” phenomenon of deep learning, as well as the lack of mathematical transparency in the complex computations. \cite{Zhang2022} Uniquely however, graph based deep learning holds the natural capability to represent a user interactions (often represented as a bipartite graph). Continuous studies on graph-based learning have allowed for machine learning methods to come to light and are widely used for their modeling capabilities. \cite{Gao22} This method has not only changed the face of music recommendations, but it has also been used in other fields of research; from ETA prediction \cite{derrow2021eta} to molecular structure prediction \cite{li2009automated}. There have been numerous graph based recommendation methods have demonstrated there applicability in the music industry as well by utilizing common MRS data sets to preform a variety baseline evaluation measurements.\cite{li2020quaternion}\cite{fan2020relation}\cite{he2020mining}

A multimedia specialist and professor at Johannes Kepler University, Markus Shedl, offers a modern perspective on music recommendation systems by mentioning, “neural network architectures are still surprisingly sparsely adopted for music recommendation systems, even though the number of respective publications is increasing." \cite{Schedl2022} Furthermore, there has discussion of the apparent lack of established multi-modal data sets similar to the Million Song data set (MSD) \cite{bertin2011million} or the LFM-1b \cite{Schedl2016}. The lack of variety from within data sets, paired the large variety evaluation metrics within music recommendation research, makes the ability to reproduce published experiments or compare models proves to be quite challenging.

This high-level overview and structural breakdown of some modern music recommendation systems identifies the fundamentals needed to understand how new approaches, like graph neural networks in music recommendation are being addressed. With the paring of graph neural networks music recommendation systems have seen a lot of performance increase, yet many models are not evaluating there models on adequately large data sets to validate and exercises new graph based recommendation algorithms. In the following section, this thesis will address the simple objectives of the paper pertaining to this topic.

\subsection{DGL LFM1b}
The academic community of MIR has many available research data sets, however many of the collections are not suitable for music recommendation research. This leaves MIR researchers with a small collection of data sets for music recommendation research. Two of the most common music recommendation data sets, MSD \cite{bertin2011million} and Last FM \cite{dieleman2011audio}. These collections are often utilized in music recommendation research as they are easily accessible, and many industries outside of MIR  use the data for model evaluation. 

However, due to their lack of robustness, many researchers are not willing to utilize these data sets, as they may require more information besides what is offered in the original collection. In particular, for the Last FM data set, there exists a larger parent collection of sparse listening event histories for users. This data set is known as the LastFM1b data set \cite{Schedl2016}.

The LastFM1b is a collection of more than one billion listening events, intended to be used for various music retrieval and recommendation tasks. Specifically, LastFM1b provides more types of information on users and their listening behaviors that many other data sets do not provide. This additional information provides listening behaviors marked by timestamp for user interactions with additional types of entities (albums, tracks). 

With the understanding that music recommendation research on graph-based networks is not utilizing the LastFM1b dataset to evaluate their model's ability to generalize over heterogeneous graphs, but rather is using the smaller LastFM collection. It is worth exploring the capabilities and limits of utilizing more information than just users, artists, and tags in the case of the LastFM data set. Additionally, the popularity of deep learning with graphs to surely increase in the following years. This thesis will aim to create an optimized custom data set loaded for the LastFM1b, allowing researchers to easily acquire the necessary heterogeneous network that is required for graph-based deep learning research on the LastFM1b data set.

\subsection{Graph Based Deep Learning for Link Prediction}
As the development of deep learning in recommendation has seen a massive increase in novel graph based algorithms,  there has not been ample support by the MIR community to challenge, discuss or build their own implementations of novel deep learning algorithms for music recommendation. \cite{Schedl2022} \cite{Gao22} As mentioned, there is not much support for MRS deep learning research, so utilizing deep learning to contribute to the slowing research in music recommendation is required to maintain the topic's relevancy in the coming years. 

Among the novel recommendation algorithms, specifically within the field of deep learning, graph based learning methods have been shown to perform competitively against mode traditional recommendation methods.\cite{Gao2021} Therefore, with the knowledge of deep learning in MRS slowing \cite{Schedl2022}, and the successful graph based learning methods have shown in previous MRS collections, this thesis will aim to deploy Graph Neural Network models to perform heterogeneous link prediction on the LastFM1b data set. The models that will be attempted will be link prediction of user to track, user to album, and user to artist edges. 

\subsection{Beyond Accuracy Evaluation}

As link prediction is a common task for graph representation learning problems. As is the case link prediction is comparatively similar to recommendation systems. This thesis will conclude the contributions by applying the designed framework, and data set,  by implementing a  recommendation algorithm utilizing the resulting link prediction models and performance measures. From these recommendation algorithms, the collected information will allow for conclusions on the generated models utilizing the novel data set loader. 

These conclusions will offer further insight into not just the LastFM1b data set but user behavior that is learned to create the mentioned link prediction models. Additionally, there will be a discussion on evaluations of the proposed recommendation system. This paired with some non-accuracy statistics should proved additional insights into such measurements of diversity, novelty, and coverage to maintain interesting and relevant recommendation systems
