\section{LastFM1b Data Loader}

\subsection{Preliminary Findings}

From the data loader, there have been a significant amount of findings and logistic barriers that are most definitely worth mentioning a preliminary results section.

From the multiple modes of the LastFM1b data loader states, when computing the full LastFM1b heterogeneous graph. Some basic count measurements can provide a few additional measurements not directly mentioned in the distributional analysis of the LastFM1b. In regard to run and storage time, the time it takes to fully compile a graph is about ~3hours, as there are a significant amount of bad instances that exist within the LastFM1b. 

\begin{table}[!ht]
\renewcommand{\arraystretch}{1.50}
\caption{The number of nodes the full LFM1b data loader can capture}
\label{tablePCA}
\centering
\begin{tabular}{| c | c |}
\hline
\bfseries Node Type & \bfseries Number of Nodes \\
\hline\hline
User & (~120K)  \\
\hline
Artsit & (~3M)\\
\hline
Album & (~15M)  \\
\hline
Track & (~32M)  \\
\hline
Genre & (21)  \\
\hline
\end{tabular}
\end{table}

\begin{table}[!ht]
\renewcommand{\arraystretch}{1.50}
\caption{The number of edges the full LFM1b data loader can capture}
\label{tablePCA}
\centering
\begin{tabular}{| c | c |}
\hline
\bfseries Edge Type (no reverse edges) & \bfseries Number of Edges \\
\hline\hline
User -> Artist & (61411336)  \\
\hline
User -> Album & (?)\\
\hline
User -> Track & (?)  \\
\hline
Artist -> Genre & (414379)  \\
\hline
Album -> Artist & (14184326)  \\
\hline
Track -> Artist & (27258365)  \\
\hline
\end{tabular}
\end{table}

From these findings you can observe the first barrier as not being able to find the number of edges that exist between user and track, user, and album. While this is the correct assumption, I rather just have not had time to compute these individual statistics due to large amount of computational time it takes to compile the full graph, even without the metapath2vec module.

Additionally, it should be noted that when using metapath2vec, there are tremendous allocation errors due to the necessary storage required to store a graph representation in local CPU memory. To account for this, the subset module was utilized to not only split the graph by node types if desired but specify the number of users to collect for a compiled interaction graph. Since users have the most edges and inter connections within the LastFM1b data set, this adjustment significantly reduces the allocation space required to compile a full graph.

However, in many, if not most cases, the number of users has to be below 50 to compute a full compiled graph with metapath2vec node embedding representations. Though this is a significant reduction of the information provided in the usable number of users for link prediction and recommendation. There is no sacrifice on the number of artists, albums, or tracks available in the graph, for any subset. This, paired with the subset model, which when N users are specified, finds users to maintain the original demographic distribution of the original LastFM1b data set prevents as much information loss by making a subset as possible.

Yet another major barrier for this data loader, finds another allocation error when computing graphs that utilize more than one node type, ergo a LastFM1b data set of artists and tracks, artists, and albums, or just albums, or just tracks for any specified number of users. This has been the most significant
barrier for provided quality, non-preliminary results on the deep graph library data loader.

Since the data loader works, but the allocation errors prove to be cumbersome, this evaluation of the thesis may possibly be inconclusive if additional storage space is not reallocated permitted to be utilized for this research project.

As a result, from these limitations, the data loader though not able to compile the full graph, has found ample space to create a compiled version of itself, if and only if the following is used: a small number of users, artists, and genres. Though this graph prevents further analysis on the unique impact of adding tracks or albums music recommendation graphs, it is still able to compute information on one of the data loading subsets that can be utilized for one type of link prediction model that we be attempted later.


