
\chapter{Results}   
As a continuation from the methodologies and approach of the thesis. The results chapter will offer further technical insight into the findings from the methods chosen. Specifically, when computing the data loader for the LastFM1b, the results of the approach should present the findings from compiling such a large  data collection. Outlining the amount of information loss, the total number of edges, nodes, and connections in the graph. As well as information concerning storage space, and time it takes to compile a full heterogeneous graph into memory.

Secondly the findings from the link prediction models should be presented. The parameters chosen for the best preforming models should be outlined, and the methods for tuning the models should be noted. Since this also a comparative study between the RHGNN and RGCN models, so listing the performance of the models for the data collection should be outlined, as well as interpreted.

Additionally, the different subsets capable of being computed from the LastFM1b data set should be utilized for additional comparisons for further validation of the LastFM1b data set as this thesis aims to justify the need for additional contextual and semantic information utilized for music recommendation 

Finally, the findings from the recommendations computations should be discussed. As this is not a recommendation performance analysis, accuracy of the recommendations will not be the only covered evaluation metric. Rather all the evaluation measures as mentioned in the methods chapter should be applied to outline interpretative results and offer insights on the link prediction models.

\input{results/LastFM1bDataLoader}
\input{results/LastFM1bLinkPrediction}
\input{results/LFM1bRecommendation}

\newpage


