\chapter{Conclusions}

From the preliminary findings the are some key observations that can be made from each of the results sections. In sequential order, the data loader provides optimal flexibility and customize to provide transparency into the programs architecture. The final compiled graph from the data loader removes a significant amount of artists, albums, and tracks. However, the information loss is reduced to a minimum with much of the information retained in the resulting fully connected graph.

The data loader has been tested for optimal performance, and adjusted to utilize fast computation methods. As mentioned, all the the data cleaning and preparation has been compiled from this data set to fit in a ~5GB binary output file. Additionally, once compiled the graph can run multiple post processing operations that do not include filtering through the raw input files. As seen the data loader has a significant amount of adjustments to account for. The promised information that can be acquired from the implementation, while can be acquired, is not efficient enough to be ran on the research device that the data loader was built with. Therefore, as mentioned, many of the subsets that were capable of being compiled could be fit into memory to be validated through model testing.


The link models and recommendation algorithm followed this limited result with similar barriers. Without the necessary information to compute link prediction models, it was not possible to preform the necessary recommendation. As mentioned however, there was one subset and one model to be computed. Given the full LastFM1b graph, with users artists, and genres. The user to artist link prediction model that was given the proper compiled information was able to preform a very high level in both the implemented model (RHGNN) and outsourced model (RGCN). To also note the comparison of the models performance, it provides additional justification to the results found in the RHGNN paper. This is because in the RHGNN paper there was a high performance measured for the proposed model, than that of the RGCN model.

However, to conclude upon the recommendations of this model is challenging for two distinct reasons. The first being that the models' performance whilst effective and notably optimistic, there are some significant factors that need to be validated before such a high performing result is excepted. Secondly, the recommendation algorithm whilst working does not have evaluation metrics like diversity, novelty, coverage, or accuracy to evaluate the true performance of the single models recommendation performance.

Lastly, it is difficult to believe that there will be capabilities to perform multi-target recommendation with compiled forms of subsets with more contextual and semantic information that just users, artists, and genres.

\input{conclusions/Discussion}
\input{conclusions/Future_Work}

\newpage