\chapter{Methods}
Form the understandings of modern graph based deep learning music recommendation systems, as well the known limitations that are associated with these approaches as they relate to music recommendation systems, this chapter will address the technical specifics to form methodology of the thesis.

Firstly, this methodology section will outline the known data that will be utilized for the thesis. The LastFM1b data set will be formally introduced with the distributional analysis conducted by the published paper, as well as some additional supplementary information on converting the data into a data loader for the specified framework.

Recalling the state of the art chapter, this methodology will summarize the models selected to be used for testing. As well as offer insights into heterogeneous graph neural networks and how they specific pertain to music recommendation.

As training for link prediction is a unique approach in graph based machine learning, the chapter will continue into discussing how these models will be trained. In doing, so the chapter will address how recommendation applies to this method of prediction, and how it can be utilized in the context of music recommendation for the LastFM1b data set. Specifically, the recommendation model will utilize three different link prediction models for scoring likely interactions among users and unseen tracks, albums, and artists.

Finally these approaches will need to be qualitatively and quantitatively justified, the chapter will finish by providing insights on the evaluation metrics utilized to interpret the performance of the LFM1b data set loader, the link prediction models, as well as the results from the recommendations provided from the link prediction models. 


\input{methods/DGL_LFM1b_Dataset}
\input{methods/Models}
\input{methods/Training}
\input{methods/Link_Prediction}
\input{methods/Music_Recommendation}
\input{methods/Evaluation}





\newpage
